---
title: "graphics with ggplot"
author: "maddie"
date: "19 June 2019"
output: html_document
---
# # Learning ggplot2

We're learning ggplot2 It's going to be amazing. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
```{ohi_data <- read_csv("https://raw.githubusercontent.com/OHI-Science/data-science-training/master/data/OHI_global_data.csv")}
``` 

```{r start ggplot}
ggplot(data = ohi_data, aes(x = georegion_one, y = OHI_score)) + 
  geom_point()

ggplot(data = ohi_data, aes(x = georegion_one, y =OHI_score)) + 
  geom_jitter(width=0.2)

```
boxplot 
```{}
ggplot(data=ohi_data, aes (x=georegion_one)) +
  geom_bar()
```
histogram 
```{}
ggplot(data=ohi_data, aes (x=HDI)) +
  geom_histogram()
```
multiple geoms exploration 
```{}
ohi_summary <- read_csv("https://raw.githubusercontent.com/OHI-Science/data-science-training/master/data/OHI_scores_georegion_summary.csv")

ohi_summary
```
you need the identity here for the value of the y axis 
```{}
ggplot(data = ohi_summary, aes(x = georegions, y = OHI_score_average)) + 
  geom_bar(stat="identity") + 
  geom_jitter(data=ohi_data, aes(x=georegion_one, y=OHI_score))

``` 
trying to see if these are different 
```{}
ggplot(data = ohi_data, aes(y=OHI_score, x = HDI, color=georegion_one)) +
  geom_point()
``` 
versus 
```{}
ggplot(data = ohi_data) +
  geom_point(aes(y = OHI_score, x = HDI, color=georegion_one))
``` 
they are indeed the same result 
typically if you have a lot of layers its better to add asthetics in the geom rahter than in the ggplot because you can get confused with the local and global layers, you can also work on the nuances layers better in the geompoint because you can choose more here. 

asthetics: 
you can assign your x and y axis to vairables in your dataset, but can do heaps more 


changing the point size: 
```{}
ggplot(data = ohi_data, aes(x = OHI_score, y = HDI, size = coastal_pop)) + 
  geom_point()
  
  ggplot(data = ohi_data, aes(x = OHI_score, y = HDI, color = coastal_pop)) + 
  geom_point()
  

```
Themes: 
```{}
ggplot(data = ohi_data, aes(x = OHI_score, y = HDI)) + 
geom_point() + 
theme_bw()
``` 
  
```{}
source('https://raw.githubusercontent.com/OHI-Science/ohiprep/master/src/R/scatterTheme.txt')       

ggplot(data = ohi_data, aes(x = OHI_score, y = HDI)) + 
  geom_point() + 
  scatterTheme
``` 

```{}
install.packages("RColorBrewer")
library(RColorBrewer)
display.brewer.all()

ggplot(data = ohi_data, aes(x = OHI_score, y = OHI_trend, color= HDI)) + 
geom_point(size = 3) + 
scale_color_gradientn(colors = c("blue", "red"))

``` 
